HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications

### 2018-07-25 scnn.tex
smaller sphere figures

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{sphere_grids}
	\caption{Two realizations of a grid on the sphere. Left: the equirectangular grid, using equiangular spacing in a standard spherical-polar coordinate system. Right: An equiangular cubed-sphere grid, as described in \citet{ronchi1996cubed}. Figure from \citet{boomsma2017spherical}.}
	\label{fig:sphere_grids}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{half_graph_4}
	\caption[]{Graph built from an HEALPix pixelization of half the sphere ($N_{side} = 4$). By construction, each node has 8 neighbors, except the highlighted ones which have only 7.\footnotemark[6]}
	\label{fig:healpix_graph_4}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[height=7em]{sphere_grid_equirectangular}
	\hfill
	\includegraphics[height=7em]{sphere_grid_cubedsphere}
	\hfill
	\includegraphics[height=7em]{half_graph_4}
	\caption[]{Some pixelizations of the sphere. Left: the equirectangular grid, using equiangular spacing in a standard spherical-polar coordinate system. Middle: an equiangular cubed-sphere grid, as described in \citet{ronchi1996cubed}. Right: graph built from an HEALPix pixelization of half the sphere ($N_{side} = 4$). By construction, each node has 8 neighbors, except the highlighted ones which have only 7.\footnotemark[7] Left and middle figures are taken from \citet{boomsma2017spherical}.}
	\label{fig:sphere_grids}
	\label{fig:healpix_graph_4}
\end{figure}

@@

@@
